The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-11 article.tex
Cite RDKit/Open Babel

\subsection*{Table 5 - SMARTS matching performance.}\label{tab:smigrep}
  Total time taken to match the SMARTS \texttt{O=[C,N]aa[N,O;!H0]} against $\sim$1.5 million SMILES from
  ChEMBL 21. The reported time is for single core execution, measure with the Unix time utility (Cent OS 7, Intel Core i7-4790 CPU @ 3.60GHz). The times for recent versions of OpenBabel and RDKit are included for reference but this is not intended to be a systematic comparison. The difference in number found is due to variations in valence and aromaticity models.
  \vskip \baselineskip

\begin{tabular}{lll}
Toolkit                   & Time   & Matched \\
\hline
CDK 1.4.9                 & 64m3s  & 69,782  \\
CDK \cdkversion{}         & 1m7s   & 62,518  \\
OpenBabel 2.3.90          & 13m55s & 61,906  \\
RDKit 2016.3.4            & 6m18s  & 62,402  \\
\end{tabular}

>>>>

\subsection*{Table 5 - SMARTS matching performance.}\label{tab:smigrep}
  Total time taken to match the SMARTS \texttt{O=[C,N]aa[N,O;!H0]} against $\sim$1.5 million SMILES from
  ChEMBL 21. The reported time is for single core execution, measure with the Unix time utility (Cent OS 7, Intel Core i7-4790 CPU @ 3.60GHz). The times for recent versions of Open Babel~\cite{OBoyle2011} and RDKit~\cite{rdkit} are included for reference but this is not intended to be a systematic comparison. The difference in number found is due to variations in valence and aromaticity models.
  \vskip \baselineskip

\begin{tabular}{lll}
Toolkit                   & Time   & Matched \\
\hline
CDK 1.4.9                 & 64m3s  & 69,782  \\
CDK \cdkversion{}         & 1m7s   & 62,518  \\
Open Babel 2.3.90         & 13m55s & 61,906  \\
RDKit 2016.3.4            & 6m18s  & 62,402  \\
\end{tabular}
